### 2014-12-16 text/AppendixA.tex

This appendix gives full typing derivations for the examplespresented in Chapter~\ref{ch:applications},
which demonstrate simple coeffect calculi for implicit parameters, liveness and data-flow.

>>>>

This appendix gives full typing derivations for the examples presented in Chapter~\ref{ch:applications},
which demonstrate simple coeffect calculi for implicit parameters, liveness and data-flow.
